Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-15 icse/paper.tex
Made table nice

\begin{table}[]
\centering
\begin{tabular}{@{}llll@{}}
\toprule
\textit{\textbf{Relation}} & \textit{\textbf{\begin{tabular}[c]{@{}l@{}}Maintainability\\ Score\end{tabular}}} & \textit{\textbf{\begin{tabular}[c]{@{}l@{}}Number of\\ Refactorings\end{tabular}}} & \textit{\textbf{\begin{tabular}[c]{@{}l@{}}Percentage of\\ Refactorings\end{tabular}}} \\ \midrule
\textbf{Common Hierarchy} & \textbf{0,51} & \textbf{792} & \textbf{20,9\%} \\ \midrule
Sibling & 0.57 & 637 & 16,8\% \\
\rowcolor[HTML]{FFCCC9}
Same Hierarchy & 0,55 & 22 & 0,6\% \\
\rowcolor[HTML]{FFCCC9}
Superclass & 0,20 & 74 & 2,0\% \\
\rowcolor[HTML]{FFCCC9}
First Cousin & -0,02 & 53 & 1,4\% \\
\rowcolor[HTML]{FFCCC9}
Ancestor & -0,65 & 6 & 0,2\% \\ \midrule
\textbf{Common Class} & \textbf{0,01} & \textbf{2025} & \textbf{53,5\%} \\ \midrule
Same Method & 0,01 & 762 & 20,1\% \\
Same Class & 0,01 & 1263 & 33,3\% \\ \midrule
\textbf{Unrelated} & \textbf{-0,02} & \textbf{688} & \textbf{18,2\%} \\ \midrule
No Direct Superclass & 0,08 & 289 & 7,6\% \\
External Superclass & -0,02 & 225 & 5,9\% \\
\rowcolor[HTML]{FFCCC9}
No Indirect Superclass & -0,04 & 30 & 0,8\% \\
External Ancestor & -0,26 & 144 & 3,8\% \\ \midrule
\textbf{Common Interface} & \textbf{-0,11} & \textbf{283} & \textbf{7,5\%} \\ \midrule
Same Direct Interface & 0,02 & 160 & 4,2\% \\
Same Indirect Interface & -0,31 & 123 & 3,2\%
\end{tabular}
\caption{Influence on maintainability of refactoring clones by certain relations.}
\label{tab:relation_refactor}
\end{table}

>>>>

\begin{table}[]
\centering
\begin{tabular}{@{}llll@{}}
\toprule
\textit{\textbf{Relation}} & \textit{\textbf{\begin{tabular}[c]{@{}l@{}}Maintainability\\ Score\end{tabular}}} & \textit{\textbf{\begin{tabular}[c]{@{}l@{}}Number of\\ Refactorings\end{tabular}}} & \textit{\textbf{\begin{tabular}[c]{@{}l@{}}Percentage of\\ Refactorings\end{tabular}}} \\ \midrule
\textbf{Common Hierarchy} & \textbf{0,51} & \textbf{792} & \textbf{20,9\%} \\ \midrule
\hspace{10pt} Sibling & 0.57 & 637 & 16,8\% \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} Same Hierarchy & 0,55 & 22 & 0,6\% \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} Superclass & 0,20 & 74 & 2,0\% \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} First Cousin & -0,02 & 53 & 1,4\% \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} Ancestor & -0,65 & 6 & 0,2\% \\ \midrule
\textbf{Common Class} & \textbf{0,01} & \textbf{2025} & \textbf{53,5\%} \\ \midrule
\hspace{10pt} Same Method & 0,01 & 762 & 20,1\% \\
\hspace{10pt} Same Class & 0,01 & 1263 & 33,3\% \\ \midrule
\textbf{Unrelated} & \textbf{-0,02} & \textbf{688} & \textbf{18,2\%} \\ \midrule
\hspace{10pt} No Direct Superclass & 0,08 & 289 & 7,6\% \\
\hspace{10pt} External Superclass & -0,02 & 225 & 5,9\% \\
\rowcolor[HTML]{FFCCC9}
\hspace{10pt} No Indirect Superclass & -0,04 & 30 & 0,8\% \\
\hspace{10pt} External Ancestor & -0,26 & 144 & 3,8\% \\ \midrule
\textbf{Common Interface} & \textbf{-0,11} & \textbf{283} & \textbf{7,5\%} \\ \midrule
\hspace{10pt} Same Direct Interface & 0,02 & 160 & 4,2\% \\
\hspace{10pt} Same Indirect Interface & -0,31 & 123 & 3,2\%
\end{tabular}
\caption{Influence on maintainability of refactoring clones by certain relations.}
\label{tab:relation_refactor}
\end{table}
